### 2017-08-21 README.Rmd
update readme

@@

General questions should be asked on the
[Bioconductor support forum](https://support.bioconductor.org/), using
`MSnbase` to tag the question. Feel also free to open a GitHub
[issue](https://github.com/lgatto/MSnbase/issues).

>>>>

To get an overview of the package, see
the
[*MSnbase-demo*](https://lgatto.github.io/MSnbase/articles/MSnbase-demo.html) vignette. More
vignettes are available in the *Articles* tab.

@@

General questions should be asked on
the [Bioconductor support forum](https://support.bioconductor.org/),
using `MSnbase` to tag the question. Feel also free to open a
GitHub [issue](https://github.com/lgatto/MSnbase/issues), in
particular for bug reports.
